### 2024-08-18 JOSS/paper.rmd
Add files via upload

---
title: 'pyTopoComplexity: A Python package for topographic complexity analysis'
tags:
  - Python
  - topographic complexity
  - surface roughness
  - two-dimensional continuous wavelet transform
  - fractal dimension
  - rugosity index
authors:
  - name: Larry Syu-Heng Lai
    corresponding: true
    orcid: 0000-0003-4589-9729 
    affiliation: "1"
  - name: Adam M. Booth
    orcid: 0000-0002-7339-0594   
    affiliation: "2"
  - name: Alison R. Duvall
    orcid: 0000-0002-7760-7236 
    affiliation: "1"
  - name: Erich Herzig
    orcid: 0000-0002-3898-5971 
    affiliation: "1"
affiliations:
 - name: Department of Earth and Space Sciences, University of Washington, Seattle, Washington, USA
   index: 1
 - name: Department of Geology, Portland State University, Portland, Oregon, USA
   index: 2
date: 31 August 2024
bibliography: paper.bib
---

# Summary

**pyTopoComplexity** is a Python package that provides a computationally efficient and highly 
customizable implementation of three methods for quantifying topographic complexity. 
These methods include two-dimensional continuous wavelet 
transform (2D-CWT) analysis, fractal dimension estimation, and rugosity index calculation across 
various spatial scales. This package addresses the scarcity of open-source software for these 
sophisticated methods, which are crucial in modern terrain analysis, and facilitates data 
comparison and reproducibility. In the [software respository](https://github.com/GeoLarryLai/pyTopoComlexity.git), 
we also include a Jupyter Notebook file that integrates components from the Python-based 
surface-process modeling platform **Landlab** [@Hobley2017]. This allows researchers to 
simulate the smoothing of topography over time through terrestrial nonlinear hillslope 
diffusion processes. By combining these features, **pyTopoComplexity** advances the toolset 
available to researchers for measuring and simulating the time-dependent persistence of 
topographic complexity signatures against environmental forces on terrain surfaces.

# Statement of need

Topographic complexity, often referred to as topographic roughness or surface roughness, provides 
critical insights into surface processes and the interactions among the geosphere, biosphere, and 
hydrosphere. With the increasing availability, utility, and popularity of digital terrain model (DTM) 
data, quantifying topographic complexity has become an essential measure in terrain analysis across 
various research fields. This necessity spans applications such as terrain classification and mapping 
at various spatial scales [@Weiss2001; @Robbins2018; @Lindsay2019; @PardoIguzquiza2022a], evaluating 
the depositional age of event sedimentation and subsequent erosion processes 
[@Hetz2016; @Johnstone2018; @Booth2017; @LaHusen2020; @Herzig2023], and identifying habitats to assess 
ecological diversity on land and seafloor [@Frost2005; @Hetz2016; @Wilson2007].

In recent years, several advanced methods for quantifying topographic complexity have been developed, 
including two-dimensional continuous wavelet transform (2D-CWT) analysis [@Booth2009; @Berti2013], 
fractal dimension estimation [@Taud2005; @Robbins2018; @PardoIguzquiza2020], and rugosity index 
calculation [@Jenness2004; @DuPreez2015]. These methods are considered more effective for terrain analysis 
tasks compared to conventional morphological metrics such as variations in local slope and relief. 
Despite their importance, comprehensive publicly available tools that incorporate these advanced 
methods for studying topographic complexity are lacking. Common open-source geospatial analysis software, 
such as QGIS [@QGIS_software], GRASS GIS [@GRASS_GIS_software], and WhiteboxTools [@Lindsay2016], only 
implement basic conventional methods, limiting the reproducibility and comparability of these newer 
approaches. Although some specialized programs for calculating the rugosity index exist [@Walbridge2018; @Benham2022], 
they have been limited to marine bathymetric studies and involve various mathematical choices and designs.

To address this gap, we have developed an open-source Python toolkit called **pyTopoComplexity**, which provides 
computationally efficient and easily customizable implementations of three modules for performing and 
visualizing the results of 2D-CWT, fractal dimension, and rugosity calculations (Table 1\autoref{tab:1}). 
This toolkit can detect the grid spacing and unit of the projected coordinate system (acceptable in meters, 
U.S. survey feet, and international feet) from the input raster DTM file (GeoTIFF format) and 
automatically conduct unit conversions in necessary calculation steps to ensure data consistency and 
reproducibility. Results at nodes affected by edge effects due to no-data values outside the input raster 
will be removed by default. Users can define the suitable spatial scale to match their research purposes 
and choose computational approaches (e.g., chunk processing, faster mathematical approximations) to 
optimize performance (see details in the **Methods and features overview** section).

| Modules  | Classes | Method Descriptions | References |
| ------------- | ------------- | ------------- | ------------- |
| pycwtmexhat.py | CWTMexHat | Quantifies the wavelet-based curvature of the land surface using two-dimensional continuous wavelet transform (2D-CWT) with a Mexican Hat wavelet | @Booth2009; @Booth2017 |
| pyfracd.py | FracD | Conducts fractal dimension analysis on the land surface using variogram procedures | @Wen1997; @PardoIguzquiza2020|
| pyrugostiy.py | RugosityIndex | Calculates the rugosity index of the land surface | @Jenness2004; @DuPreez2015 |
Table: Table 1 \label{tab:1}: Modules contained in the **pyTopoComplexity** package.

Each module of the **pyTopoComplexity** is provided with a corresponding [example Jupyter Notebook file](https://github.com/GeoLarryLai/pyTopoComlexity/tree/main/example) 
for usage instructions, using the Light Detection and Ranging (LiDAR) DTM data of a deep-seated landslide that 
occurred in 2014 in the Oso area of the North Fork Stillaguamish River valley, Washington State, USA 
[@WashingtonGeologicalSurvey2023]. In the software repository, we also include an additional Jupyter Notebook file 
[**nonlineardiff_Landlab.ipynb**](https://github.com/GeoLarryLai/pyTopoComlexity/blob/main/example/nonlineardiff_Landlab.ipynb), 
which allows researchers to simulate the smoothing of topography over time via terrestrial nonlinear hillslope 
diffusion processes [@Roering1999]. This is achieved by employing the `TaylorNonLinearDiffuser` module from the 
`terrainBento` Python package [@Barnhart2019] and running the simulation in the **Landlab** environment [@Hobley2017].

By bridging the gap between different advanced terrain analytical approaches and incorporating functionality 
for landscape evolution modeling, **pyTopoComplexity** serves as a valuable resource for topographic complexity 
research and has the potential to foster new insights and interdisciplinary collaborations in the fields 
of geology, geomorphology, geography, ecology, and oceanography.

# Methods and features overview

## Two-dimensional continuous wavelet transform analysis

The **pycwtmexhat.py** module in **pyTopoComplexity** implements the 2D-CWT method for terrain analysis, providing detailed information on how 
amplitude is distributed across spatial frequencies at each position in the data by transforming spatial data into position-frequency 
space. This method is particularly effective for depicting the Laplacian of topography [@Torrence1998; @Lashermes2007], revealing 
concave and convex regions of topography at various scales [@Malamud2001; @Struble2021], identifying deep-seated landslides 
[@Booth2009; @Berti2013], and estimating the depositional ages of landslide deposits [@Booth2017; @LaHusen2020; @Underwood2022; @Herzig2023].

The 2D-CWT is computed by convolving the elevation data $z$ with a wavelet family $\psi$, using a wavelet scale parameter $s$ at every location ($x$, $y$):

$$
C (s, x, y) = \Delta^2 \int_{-\infty}^{\infty} \int_{-\infty}^{\infty} z(x, y) \psi \left( x, y \right) dx \, dy
$$

, where the resultant wavelet coefficient $C(s,x,y)$ provides a measure of how well the wavelet $\psi$ matches the data $z$ at each grid [@Torrence1998]. 
When $s$ is large, $\psi$ is spread out, capturing long-wavelength features of $z$; when $s$ is small, $\psi$ becomes more localized, making it sensitive 
to fine-scale features of $z$. In this implementation, we use the 2D Mexican Hat wavelet (i.e., Ricker wavelet) function to define $\psi$:

$$
\psi = − \frac{1}{\pi(s\Delta)^4}(1-\frac{𝑥^2+𝑦^2}{2s^2})e^{(-\frac{𝑥^2+𝑦^2}{2s^2})}
\:\:\:\:\:\:\:\:\:
\lambda=\frac{2\pi s}{\sqrt{5/2}}\Delta
$$

The Mexican hat wavelet is proportional to the second derivative of a Gaussian envelope, with its Fourier wavelength ($\lambda$) 
ependent on the grid spacing ($\Delta$) of the input DTM raster. The wavelet function $\psi$ is scaled according to the 
wavelet scale parameter $s$ and the grid spacing $\Delta$, ensuring that the resultant wavelet coefficient $C$ signifies 
concave and convex landforms corresponding to the wavelet scale $s$. Users can define the value of $\lambda$ in meters as the 
targeted spatial scale for landform roughness analysis, and the **pycwtmexhat.py** module will automatically compute the wavelet 
scale $s$ based on the grid spacing ($\Delta$) of the input raster file (Figure 1)\autoref{fig:1}.

We note that the $C$ and $\psi$ equations presented here are the mathmetical approaches adapted in later publications 
[@LaHusen2020; @Underwood2022; @Herzig2023] and ongoing works [@Booth2023; @Lai2023; @Ozioko2023] of landslide mapping and 
age dating studies, with minor differences from the earlier similar research in @Booth2009 and @Booth2017 (original MATLAB codes 
available from [Booth's personal website](https://web.pdx.edu/~boothad/tools.html)). These differences in methatical approach 
can result $C$ values in different units and order of magnitude (e.g., $10^{-3}$ to $10^{-4}$ [m$^{-2}$] in @Booth2017 
and prior studies; $10^{-2}$ to $10^{-3}$ [m$^{-1}$] in @LaHusen2020 thereafter). Despite this discrepency, the $C$ values 
yielded from these two approaches are linearly scaled and interconvertible, and they both reflect identical spatiotemporal patterns 
of topographic complexity (i.e., surface roughness).

![Figure 1. Hillshade map of the 2014 Oso Landslide region (upper-left) and the results of the two-dimensional continuous wavelet 
transform (2D-CWT) analysis using the **pycwtmexhat.py** module, with designated Fourier wavelengths ($\lambda$) of the Mexican Hat 
wavelet at 15 m, 30 m, 45 m, 60 m, and 75 m. \label{fig:1}](fig1-pycwtmexhat.png){ width=100% }

## Fractal dimension analysis

The **pyfracd.py** module in **pyTopoComplexity** calculates the fractal dimension, which measures the fractal characteristics of natural 
features [@Mandelbrot1983]. This method provides insights into the self-similarity of landscapes, helping quantify their irregularity 
and fragmentation, which is crucial for studying the surface processes that shape Earth and planetary surfaces [@Xu1883].

In this module, we adapt the variogram method to estimate the local fractal dimension within a moving window centered at each cell of 
the DTM [@Taud2005; @PardoIguzquiza2020; @PardoIguzquiza2022a]. This approach simplifies the problem to estimating the fractal dimension 
of one-dimensional topographic profiles [@Dubuc1989] within the two-dimensional moving window. For a one-dimensional profile of length $L$, 
the variogram $\gamma_1(k)$ can be estimated at the $K$ lag distances ($K$ lag distances ($k = 1, \ldots, K$) by:

$$
\gamma_1(k) = \frac{1}{2(L-k)} \sum_{l=1}^{L-k} [Z(i) - Z(i+l)]^2
$$

, where $Z(i)$ is the elevation at location $i$ along the profile. The local fractal dimension ($FD$) is estimated from one-dimensional 
profiles in principal directions (i.e., horizontal, vertical, and diagonal) within a square moving window. Assuming that fractional 
Brownian motion is an appropriate stochastic model for natural surfaces, its variogram follows a power-law model with respect to $k$ [@Wen1997]:

$$
\gamma_1(k) = \alpha h^\beta, \quad \alpha \geq 0; \quad 0 \leq \beta < 2
$$

, and its exponent $\beta$ is related to the local fractal dimension ($FD$) by:

$$
FD = TD + 1 - \frac{\beta}{2}
$$

, where $TD$ is the topological dimension in the Euclidean space of the fractional Brownian motion. For one-dimensional fractional Brownian 
motion, $TD = 1$; thus, the fractal dimension of the two-dimensional surface $(FD)_2^*$ can be estimated as the average fractal dimension of 
the one-dimensional profiles $(FD)_1^*$:

$$
(FD)_2^* = 1 + (FD)_1^*
$$

Users can specify the size (number of grids along each edge) of the moving window to study fractal characteristics at desired spatial scales.
In addition to calculating the fractal dimension, the **pyfracd.py** module also computes reliability parameters such as standard error and 
the coefficient of determination ($R^2$) to assess the robustness of the analysis (Figure 2)\autoref{fig:2}.

![Figure 2. Hillshade map of the 2014 Oso Landslide region (upper-left), example variograms (right), and the results of Fractal Dimension 
(FD) analysis using the **pyfracd.py** module. The analysis was conducted with a designated 17 by 17 grid moving window size 
(grid spacing = 3 U.S. survey feet ≈ 0.9144 meters). \label{fig:2}](fig2-pyfracd.png){ width=100% }

## Rugosity index calculation

The **pyrugosity.py** module in **pyTopoComplexity**  measures the rugosity index of the land surface, which is widely used to assess structural 
complexity of the topography. Such method has been applied in classifying seafloor types by marine geologists and geomorphologist, small-scale 
hydrodynamics by oceanographers, and studying available habitats in the landscape by ecologists and coral biologists [@Lundblad2006; @Wilson2007].

The rugosity index is determined as the ratio of the contoured area (i.e., true geometric surface area) to the planimetric area within the square 
moving window, highlighting smaller-scale variations in surface height:

$$
\text{Rugosity Index} = \frac{\text{contoured area}}{\text{planimetric area}}
$$

This module adapts the Triangulated Irregular Networks (TIN) method from @Jenness2004 to approximate the contoured area as the sum of 
eight truncated-triangle areas. These triangles connect the central grids, four corner grids, and four grids at the middle points of the 
surrounding edges within the moving window. If no local slope correction is applied, the planimetric area is considered to be the horizontal 
planar area of the moving window, as described in @Jenness2004. Another approach considers slope correction where to the planimetric area is 
projected onto an plane of the local gradient [@DuPreez2015].

By definition, the rugosity index is as a minimum value of one (completely flate surface). Typical valuesrange of the conventional rugosity 
index (without slope correction) from one to three although larger values are possible in very steep terrains. The slope-corrected rugosity 
index, also called arc-chord ratio (ACR) rugosity index, could provide a better representation of local surface complexity (Figure 3)\autoref{fig:3}.

![Figure 3. Hillshade map of the 2014 Oso Landslide region (left), along with the calculated results of the Arc-Chord Ratio Rugosity Index (middle) 
and the conventional Rugosity Index (right), using the **pyrugosity.py** module. The calculations were performed with a designated 17 by 17 grid 
moving window size (grid spacing = 3 U.S. survey feet ≈ 0.9144 meters). \label{fig:3}](fig3-pyrugosity.png){ width=100% }

## Forward simulation of landscape smoothing through nonlinear hillslope diffusion process

The `nonlineardiff_Landlab.ipynb` notebook in the **pyTopoComplexity** package offers a sophisticated tool for simulating landscape evolution 
through nonlinear diffusion processes due to near-surface soil disturbances and downslope sediment creep [@Roering1999]. This tool runs the 
simulation in the **Landlab** environment (version >= 2.7) [@Hobley2017] with the `TaylorNonLinearDiffuser` module from the `terrainBento` 
Python package [@Barnhart2019]. The main simulation iteratively applies the nonlinear diffusion model to predict changes in surface 
elevation $z$ over time $t$:

$$
\frac{\partial z}{\partial t} = -\nabla \cdot \mathbf{q}_s
$$

, where \(\mathbf{q}_s\) represents the sediment flux at the surface. The sediment flux is further defined by a nonlinear flux law that is 
approximated using a Taylor series expansion [@Ganti2012]:

$$
\mathbf{q}_s = K \mathbf{S} \left[1 + \sum_{i=1}^N \left( \frac{S}{S_c}\right)^{2i}\right]
$$

Here, $\mathbf{S} = -\nabla z$ represents the downslope topographic gradient, and $S$ is its magnitude. The parameter $K$ is a diffusion-like 
transport coefficient with dimensions of length squared per time. The simulation also incorporates the critical slope gradient ($S_c$) to 
ensure numerical stability and prevent the numerical instability when $S = S_c$. $N$ denotes the number of terms in the Taylor 
expansion, while $i$ specifies the number of additional terms included. If $N = 1$, the expression simplifies to linear diffusion [@Culling1963]. 
The default is set to $N = 2$ that gives the behavior described in @Ganti2012 as an approximation of the nonlinear diffusion.

This notebook provides a comprehensive workflow that guides users through setting up, importing raster files, and running simulations. Since 
**Landlab** primarily handles DTM data in ESRI ASCII format, this notebook includes utility functions for converting raster files between GeoTIFF 
and ESRI ASCII formats. Users are required to specify the values for $S_c$, $K$, the length of each time step in years, and the final time to 
stop the simulation. The example included in the notebook uses LiDAR DTM data from the 2014 Oso Landslide [@WashingtonGeologicalSurvey2023], 
with parameter values provided in @Booth2017, in an attempt to reproduce the simulation results presented in that study (Figure 4\autoref{fig:4}).

![Figure 4. Hillshade map of the 2014 Oso Lanslide region and surface smoothing evolution over 15,000 years predicted by a 
nonlinear hillslope diffusion model used in the `pyrugosity` module, in attempt to reproduce the simulation results in 
@Booth2017.\label{fig:3}](fig4-smoothing.png){ width=100% }

# Acknowledgements

The development of **pyTopoComplexity** is a part of collactive effort within the [Landslide subteam](https://cascadiacopeshub.org/team-1-landslides/) of the 
[Cascadia Coastlines and Peoples Hazards Research Hub (Cascadia CoPes Hub)](https://cascadiacopeshub.org), which is supported by funds from the 
National Science Foundation Award ([#2103713](https://www.nsf.gov/awardsearch/showAward?AWD_ID=2103713&HistoricalAwards=false)). We express special thanks to 
Dr. Eulogio Pardo-Igúzquiza who shared his Fortran code for fractal dimension analysis used in his work @PardoIguzquiza2022b, which greatly inspired the development 
of **pyfracd.py** module.

The development of **pyTopoComplexity** is part of a collaborative effort within the [Landslide subteam](https://cascadiacopeshub.org/team-1-landslides/) of the 
[Cascadia Coastlines and Peoples Hazards Research Hub (Cascadia CoPes Hub)](https://cascadiacopeshub.org), funded by the National Science Foundation Award ([#2103713](https://www.nsf.gov/awardsearch/showAward?AWD_ID=2103713&HistoricalAwards=false)). 
We extend special thanks to Dr. Eulogio Pardo-Igúzquiza, who generously shared his Fortran code for fractal dimension analysis used in his work 
@PardoIguzquiza2022b, which significantly inspired the development of the **pyfracd.py** module.

# References

### 2024-08-18 JOSS/paper.rmd
Add files via upload

@@
 
-The development of **pyTopoComplexity** is a part of collactive effort within the [Landslide subteam](https://cascadiacopeshub.org/team-1-landslides/) of the 
-[Cascadia Coastlines and Peoples Hazards Research Hub (Cascadia CoPes Hub)](https://cascadiacopeshub.org), which is supported by funds from the 
-National Science Foundation Award ([#2103713](https://www.nsf.gov/awardsearch/showAward?AWD_ID=2103713&HistoricalAwards=false)). We express special thanks to 
-Dr. Eulogio Pardo-Igúzquiza who shared his Fortran code for fractal dimension analysis used in his work @PardoIguzquiza2022b, which greatly inspired the development 
-of **pyfracd.py** module.
-
 The development of **pyTopoComplexity** is part of a collaborative effort within the [Landslide subteam](https://cascadiacopeshub.org/team-1-landslides/) of the 

### 2024-08-18 JOSS/paper.rmd
Add files via upload

@@
 
-**pyTopoComplexity** is a Python package that provides a computationally efficient and highly 
-customizable implementation of three methods for quantifying topographic complexity. 
-These methods include two-dimensional continuous wavelet 
-transform (2D-CWT) analysis, fractal dimension estimation, and rugosity index calculation across 
-various spatial scales. This package addresses the scarcity of open-source software for these 
-sophisticated methods, which are crucial in modern terrain analysis, and facilitates data 
-comparison and reproducibility. In the [software respository](https://github.com/GeoLarryLai/pyTopoComlexity.git), 
+**pyTopoComplexity** is a Python package that provides a computationally efficient and customizable 
+implementation of three methods for quantifying topographic complexity. These methods include 
+two-dimensional continuous wavelet transform (2D-CWT) analysis, fractal dimension estimation, and 
+rugosity index calculation across various spatial scales. This package addresses the scarcity of 
+open-source software for these sophisticated methods, which are crucial in modern terrain analysis, 
+and facilitates data comparison and reproducibility. In the [software respository](https://github.com/GeoLarryLai/pyTopoComlexity.git), 
 we also include a Jupyter Notebook file that integrates components from the Python-based 
@@
 ensure numerical stability and prevent the numerical instability when $S = S_c$. $N$ denotes the number of terms in the Taylor 
-expansion, while $i$ specifies the number of additional terms included. If $N = 1$, the expression simplifies to linear diffusion [@Culling1963]. 
+expansion, while $i$ specifies the number of additional terms included. If $N = 0$, the expression simplifies to linear diffusion [@Culling1963]. 
 The default is set to $N = 2$ that gives the behavior described in @Ganti2012 as an approximation of the nonlinear diffusion.

### 2024-08-19 JOSS/paper.rmd
Add files via upload

@@
    index: 2
-date: 31 August 2024
+date: 18 August 2024
 bibliography: paper.bib

### 2024-08-19 pytopocomplexity/pycwtmexhat.py
Add files via upload

@@ -104,7 +104,8 @@ class CWTMexHat:
 
     def Delta_s_Calculate(self, input_dir):
         """
-        Calculate the grid spacing (Delta) and scale parameter (s) based on the input DEM.
+        1. Dxtract grid spacing (Delta) from the input DEM.
+        2. Calculate scale parameter (s) based on Delta and the user-defined Lambda
 
         Parameters:
         -----------

### 2024-08-19 pytopocomplexity/pyfracd.py

@@ -23,7 +23,7 @@ class FracD:
     Parameters:
     -----------
     window_size : int, optional
-        The size of the moving window for fractal dimension calculation. Default is 10.
+        The size of the moving window for fractal dimension calculation.
 
     Attributes:
     -----------
@@ -44,7 +44,7 @@ class FracD:
     ft2mInt : float
         Conversion factor from international feet to meters.
     window_size_m : float
-            Window size converted in meters based on grid size.
+        Window size converted in meters based on grid size.
 
     Methods:
     --------

### 2024-08-19 pytopocomplexity/pyrugosity.py

@@ -15,7 +15,11 @@ class RugosityIndex:
 
     The rugosity index is a measure of terrain complexity, calculated as the ratio of the real surface area
     to the planar area. This implementation uses a moving window approach and adapts the triangulated
-    irregular networks method described by Jenness (2004).
+    irregular networks method described by Jenness (2004). 
+    
+    If no local slope correction is applied, the planimetric area is considered to be the horizontal planar 
+    area of the moving window, as decribed in Jenness (2004). Another approach considers slope correction 
+    where to the planimetric area is projected onto an plane of the local gradient (Du Preez, 2015).
 
     Parameters:
     -----------
@@ -102,9 +106,8 @@ class RugosityIndex:
         which helps prevent numerical instability with extreme elevation differences.
         It also includes safeguards against invalid area calculations.
 
-        The surface area is approximated using 8 triangles per cell, connecting
-        the center point with its 8 neighbors. This approach is based on the method
-        described by Jenness (2004).
+        The surface area is approximated using 8 triangles per moving window, 
+        connecting the center point with its 8 neighbors, as described by Jenness (2004).
         """
         window_size = int(np.sqrt(len(values)))
         center = values[len(values) // 2]

### 2024-08-22 pytopocomplexity/pyrugosity.py
Add files via upload

@@ -322,7 +322,7 @@ class RugosityIndex:
             # Calculate window size in meters
             self.window_size_m = gridsize * self.window_size
 
-        return self.Z, self.result, self.meta, self.window_size_m
+        return self.Z, self.result, self.window_size_m
 
     def export_result(self, output_dir):
         """
@@ -390,16 +390,16 @@ class RugosityIndex:
         axes[0].set_ylabel(f'Y-axis grids \n(grid size ≈ {-round(gridsize[4],4)} [{Zunit}])')
         cbar1 = fig.colorbar(hs, ax=axes[0], orientation='horizontal', fraction=0.045, pad=0.13)
         cbar1.ax.set_visible(False)
-
-        # Plot the rugosity
-        im = axes[1].imshow(self.result, cmap='viridis')
-        im.set_clim(round(np.nanpercentile(self.result, 1), 2), round(np.nanpercentile(self.result, 99), 2))
-        
-        # Set the title based on whether slope correction was applied
+       
+        # Plot the rugosity and set the title based on whether slope correction was applied
         if self.slope_correction:
             axes[1].set_title(f'Arc-Chord Ratio (ACR) Rugosity Index\n(~{round(self.window_size_m, 2)}m x ~{round(self.window_size_m, 2)}m window)')
+            im = axes[1].imshow(self.result, cmap='viridis')
+            im.set_clim(round(np.nanpercentile(self.result, 1), 2), round(np.nanpercentile(self.result, 99), 2))
         else:
             axes[1].set_title(f'Conventional Rugosity Index\n(~{round(self.window_size_m, 2)}m x ~{round(self.window_size_m, 2)}m window)')
+            im = axes[1].imshow(self.result, cmap='plasma')
+            im.set_clim(round(np.nanpercentile(self.result, 1), 2), round(np.nanpercentile(self.result, 99), 2))
         
         axes[1].set_xlabel(f'X-axis grids \n(grid size ≈ {round(gridsize[0],4)} [{Zunit}])')
         axes[1].set_ylabel(f'Y-axis grids \n(grid size ≈ {-round(gridsize[4],4)} [{Zunit}])')

### 2024-08-22 pytopocomplexity/pytpi.py

@@ -1,0 +1,346 @@
+import os
+import numpy as np
+import rasterio
+from scipy.ndimage import uniform_filter
+import matplotlib.pyplot as plt
+from matplotlib.colors import LightSource
+from tqdm.auto import tqdm
+import dask.array as da
+from dask.diagnostics import ProgressBar
+
+class TPI:
+    """
+    A class for calculating the Terrain Position Index (TPI) of a land surface using Digital Elevation Model (DEM) data.
+
+    The Terrain Position Index (TPI) measures the topographic position of a point relative to the surrounding terrain. 
+    It determines whether a point is situated on a topographic high, low, or a slope. TPI is calculated by comparing 
+    the elevation of a cell to the mean elevation of its surrounding cells within a specified neighborhood.
+
+    In terrestrial research, TPI is commonly referred to as the ‘Topographic Position Index’ (Weiss, 2001) In oceanography and 
+    marine ecology, it is known as the ‘Bathymetric Position Index (BPI)’ (Wilson et al., 2007).
+
+    Parameters:
+    -----------
+    window_size : int, optional
+        The size of the moving window for TPI calculation. Must be an odd integer >= 3. Default is 3.
+
+    Attributes:
+    -----------
+    ft2mUS : float
+        Conversion factor from US survey feet to meters.
+    ft2mInt : float
+        Conversion factor from international feet to meters.
+    window_size : int
+        Size of the moving window for TPI calculation.
+    Z : numpy.ndarray
+        The input elevation data.
+    TPI : numpy.ndarray
+        The calculated Terrain Position Index.
+    TPIabs : numpy.ndarray
+        The absolute values of the Terrain Position Index.
+    input_dir : str
+        Path to the input DEM file.
+    window_size_m : float
+        Window size in meters.
+    meta : dict
+        Metadata of the input raster.
+
+    Methods:
+    --------
+    analyze(input_dir, chunk_processing=True, chunksize=(512, 512))
+        Perform TPI analysis on the input DEM.
+    export_result(output_dir, output_abs_dir)
+        Export the TPI and absolute TPI results to GeoTIFF files.
+    plot_result(savefig=True)
+        Plot and optionally save the original DEM, TPI, and absolute TPI results.
+
+    Example:
+    --------
+    >>> tpi = TPI(window_size=11)
+    >>> Z, TPI, TPIabs, meta, window_m = tpi.analyze('input_dem.tif')
[…]

### 2024-08-22 setup.py
Add files via upload

@@ -5,7 +5,7 @@ with open("README-pypi.md", "r", encoding="utf-8") as fh:
 
 setup(
     name="pytopocomplexity",
-    version="0.7.5",
+    version="0.8.0",
     author="Larry Syu-Heng Lai",
     author_email="larrysyuhenglai@gmail.com",
     description="A package for topographic complexity analysis",

### 2024-08-23 JOSS/paper.rmd
Add files via upload

@@
   - fractal dimension
-  - rugosity index
+  - Rugosity Index
+  - Terrain Position Index
 authors:
@@
 **pyTopoComplexity** is a Python package that provides a computationally efficient and customizable 
-implementation of three methods for quantifying topographic complexity. These methods include 
-two-dimensional continuous wavelet transform (2D-CWT) analysis, fractal dimension estimation, and 
-rugosity index calculation across various spatial scales. This package addresses the scarcity of 
-open-source software for these sophisticated methods, which are crucial in modern terrain analysis, 
-and facilitates data comparison and reproducibility. In the [software respository](https://github.com/GeoLarryLai/pyTopoComlexity.git), 
+implementation of four modern methods for quantifying topographic complexity. These methods include 
+two-dimensional continuous wavelet transform (2D-CWT) analysis, fractal dimension estimation, Rugosity 
+Index and Terrain Position Index calculations across various spatial scales. This package addresses 
+the scarcity of open-source software for these sophisticated methods, which are crucial in modern 
+terrain analysis, and facilitates data comparison and reproducibility. In the [software respository](https://github.com/GeoLarryLai/pyTopoComplexity.git), 
 we also include a Jupyter Notebook file that integrates components from the Python-based 
@@
 including two-dimensional continuous wavelet transform (2D-CWT) analysis [@Booth2009; @Berti2013], 
-fractal dimension estimation [@Taud2005; @Robbins2018; @PardoIguzquiza2020], and rugosity index 
+fractal dimension estimation [@Taud2005; @Robbins2018; @PardoIguzquiza2020], and Rugosity Index 
 calculation [@Jenness2004; @DuPreez2015]. These methods are considered more effective for terrain analysis 
@@
 implement basic conventional methods, limiting the reproducibility and comparability of these newer 
-approaches. Although some specialized programs for calculating the rugosity index exist [@Walbridge2018; @Benham2022], 
+approaches. Although some specialized programs for calculating the Rugosity Index exist [@Walbridge2018; @Benham2022], 
 they have been limited to marine bathymetric studies and involve various mathematical choices and designs.
 
-To address this gap, we have developed an open-source Python toolkit called **pyTopoComplexity**, which provides 
-computationally efficient and easily customizable implementations of three modules for performing and 
-visualizing the results of 2D-CWT, fractal dimension, and rugosity calculations (Table 1\autoref{tab:1}). 
+To address this gap, we have developed an open-source Python toolkit called **pyTopoComplexity**. This toolkit 
+offers computationally efficient and easily customizable implementations for performing and visualizing the results 
+of 2D-CWT, fractal dimension, and rugosity index calculations (see Table 1\autoref{tab:1}). Additionally, **pyTopoComplexity** 
+includes a module for calculating the Terrain Position Index (TPI), a widely used metric that is considered effective 
+in geomorphology research [@Newman2018; @Deumlich2010; @Liu2011]. The TPI is also often used alongside rugosity index 
+calculations in marine geological and ecological analyses [@Wilson2007; @Walbridge2018].
+
 This toolkit can detect the grid spacing and unit of the projected coordinate system (acceptable in meters, 
@@
 | pyfracd.py | FracD | Conducts fractal dimension analysis on the land surface using variogram procedures | @Wen1997; @PardoIguzquiza2020|
-| pyrugostiy.py | RugosityIndex | Calculates the rugosity index of the land surface | @Jenness2004; @DuPreez2015 |
+| pyrugostiy.py | RugosityIndex | Calculates the Rugosity Index of the land surface | @Jenness2004; @DuPreez2015 |
+| pytpi.py | TPI | Calculate Terrain Position Index of the land or seafloor surface | @Weiss2001; @Walbridge2018 |
 Table: Table 1 \label{tab:1}: Modules contained in the **pyTopoComplexity** package.
 
-Each module of the **pyTopoComplexity** is provided with a corresponding [example Jupyter Notebook file](https://github.com/GeoLarryLai/pyTopoComlexity/tree/main/example) 
+Each module of the **pyTopoComplexity** is provided with a corresponding [example Jupyter Notebook file](https://github.com/GeoLarryLai/pyTopoComplexity/tree/main/example) 
 for usage instructions, using the Light Detection and Ranging (LiDAR) DTM data of a deep-seated landslide that 
@@
 [@WashingtonGeologicalSurvey2023]. In the software repository, we also include an additional Jupyter Notebook file 
-[**nonlineardiff_Landlab.ipynb**](https://github.com/GeoLarryLai/pyTopoComlexity/blob/main/example/nonlineardiff_Landlab.ipynb), 
+[**nonlineardiff_Landlab.ipynb**](https://github.com/GeoLarryLai/pyTopoComplexity/blob/main/example/nonlineardiff_Landlab.ipynb), 
 which allows researchers to simulate the smoothing of topography over time via terrestrial nonlinear hillslope 
@@
 The Mexican hat wavelet is proportional to the second derivative of a Gaussian envelope, with its Fourier wavelength ($\lambda$) 
-ependent on the grid spacing ($\Delta$) of the input DTM raster. The wavelet function $\psi$ is scaled according to the 
+dependent on the grid spacing ($\Delta$) of the input DTM raster. The wavelet function $\psi$ is scaled according to the 
 wavelet scale parameter $s$ and the grid spacing $\Delta$, ensuring that the resultant wavelet coefficient $C$ signifies 
@@
 , where $TD$ is the topological dimension in the Euclidean space of the fractional Brownian motion. For one-dimensional fractional Brownian 
-motion, $TD = 1$; thus, the fractal dimension of the two-dimensional surface $(FD)_2^*$ can be estimated as the average fractal dimension of 
+motion, $TD = 1$. The fractal dimension of the two-dimensional surface $(FD)_2^*$ can be estimated as the average fractal dimension of 
 the one-dimensional profiles $(FD)_1^*$:
@@
 
-## Rugosity index calculation
+## Rugosity Index calculation
 
-The **pyrugosity.py** module in **pyTopoComplexity**  measures the rugosity index of the land surface, which is widely used to assess structural 
-complexity of the topography. Such method has been applied in classifying seafloor types by marine geologists and geomorphologist, small-scale 
+The **pyrugosity.py** module in **pyTopoComplexity**  measures the Rugosity Index of the land surface, which is widely used to assess structural 
+complexity of the topography. Such method has been applied in classifying seafloor types by marine geologists and geomorphologist, understanding small-scale 
 hydrodynamics by oceanographers, and studying available habitats in the landscape by ecologists and coral biologists [@Lundblad2006; @Wilson2007].
 
-The rugosity index is determined as the ratio of the contoured area (i.e., true geometric surface area) to the planimetric area within the square 
+The Rugosity Index is determined as the ratio of the contoured area (i.e., true geometric surface area) to the planimetric area within the square 
 moving window, highlighting smaller-scale variations in surface height:
@@
 
-This module adapts the Triangulated Irregular Networks (TIN) method from @Jenness2004 to approximate the contoured area as the sum of 
+This module adapts the Triangulated Irregular Networks method from @Jenness2004 to approximate the contoured area as the sum of 
 eight truncated-triangle areas. These triangles connect the central grids, four corner grids, and four grids at the middle points of the 
@@
 
-By definition, the rugosity index is as a minimum value of one (completely flate surface). Typical valuesrange of the conventional rugosity 
+By definition, the Rugosity Index is as a minimum value of one (completely flate surface). Typical valuesrange of the conventional rugosity 
 index (without slope correction) from one to three although larger values are possible in very steep terrains. The slope-corrected rugosity 
-index, also called arc-chord ratio (ACR) rugosity index, could provide a better representation of local surface complexity (Figure 3)\autoref{fig:3}.
+index, also called arc-chord ratio (ACR) Rugosity Index, could provide a better representation of local surface complexity (Figure 3)\autoref{fig:3}.
 
-![Figure 3. Hillshade map of the 2014 Oso Landslide region (left), along with the calculated results of the Arc-Chord Ratio Rugosity Index (middle) 
-and the conventional Rugosity Index (right), using the **pyrugosity.py** module. The calculations were performed with a designated 17 by 17 grid 
-moving window size (grid spacing = 3 U.S. survey feet ≈ 0.9144 meters). \label{fig:3}](fig3-pyrugosity.png){ width=100% }
+![Figure 3. Calculated results of the Arc-Chord Ratio Rugosity Index (upper) and the conventional Rugosity Index (lower) for the 2014 Oso Landslide 
+region, using the **pyrugosity.py** module. The calculations were performed with different moving window sizes: 17 by 17 grids (left), 49 by 49 grids 
+(middle), and 83 by 83 grids (right). Grid spacing is 3 U.S. survey feet (approximately 0.9144 meters). \label{fig:3}](fig3-pyrugosity.png){ width=100% }
+
+## Terrain Position Index calculation
+
+The **pytpi.py** module in **pyTopoComplexity** calculates the Terrain Position Index (TPI) of the land surface. The TPI, also known as the 
+Topographic Position Index in terrestrial studies [@Weiss2001], measures the relative topographic position of a point compared to its 
+surrounding landforms. This metric highlights regions that are relatively higher or lower than their surroundings, which is useful for 
+distinguishing landscape features such as hilltops, valleys, flat plains, and slopes. In oceanography, an equivalent metric is the 
+Bathymetric Position Index (BPI), which applies the TPI algorithm to bathymetric data to evaluate seafloor complexity.
+
+TPI is widely applicable for various purposes, including determining surface ruggedness [@Newman2018], classifying terrain [@zwolinski2015], 
+assessing local soil formation and hydrodynamics [@Deumlich2010; @Liu2011], and identifying habitat hotspots [@Wilson2007]. It is calculated 
+by comparing the elevation of a grid cell ($Z_{\text{grid}}$) to the mean elevation of its surrounding grid cells ($Z_{\text{neighborhood}}$) 
+within a specified neighborhood:
+
+$$
+TPI = Z_{\text{grid}} - \text{mean}(Z_{\text{neighborhood}})
+$$
+
+In this module, the TPI value is computed at the central grid within a square-shaped moving window. Users can specify the size of the moving 
+window (i.e., the number of grids along each edge) to assess the topographic position at different spatial scales. Positive TPI values 
+indicate elevated features, negative values represent depressions, and values close to zero denote flat or gently sloping areas. The **pytpi.py** 
+module also returns the absolute values of the TPI (Figure 4\autoref{fig:4}). This absolute TPI raster is suggested to be effective for 
+quick assessments in mapping and relative dating of deep-seated landslide deposits using high-resolution DTM data [@Lai2023].
+
+![Figure 4. Calculated results of the Terrain Position Index (upper) and its absolute values (lower) for the 2014 Oso Landslide region, 
+using the **pytpi.py** module. The calculations were performed with different moving window sizes: 17 by 17 grids (left), 49 by 49 grids 
+(middle), and 83 by 83 grids (right). Grid spacing is 3 U.S. survey feet (approximately 0.9144 meters). \label{fig:4}](fig4-pytpi.png){ width=100% }
 
@@
 
-The `nonlineardiff_Landlab.ipynb` notebook in the **pyTopoComplexity** package offers a sophisticated tool for simulating landscape evolution 
+The [**nonlineardiff_Landlab.ipynb**](https://github.com/GeoLarryLai/pyTopoComplexity/blob/main/example/nonlineardiff_Landlab.ipynb) notebook 
+in the **pyTopoComplexity** package offers a sophisticated tool for simulating landscape evolution 
 through nonlinear diffusion processes due to near-surface soil disturbances and downslope sediment creep [@Roering1999]. This tool runs the 
@@
 stop the simulation. The example included in the notebook uses LiDAR DTM data from the 2014 Oso Landslide [@WashingtonGeologicalSurvey2023], 
-with parameter values provided in @Booth2017, in an attempt to reproduce the simulation results presented in that study (Figure 4\autoref{fig:4}).
+with parameter values provided in @Booth2017, in an attempt to reproduce the simulation results presented in that study (Figure 5\autoref{fig:5}).
 
-![Figure 4. Hillshade map of the 2014 Oso Lanslide region and surface smoothing evolution over 15,000 years predicted by a 
-nonlinear hillslope diffusion model used in the `pyrugosity` module, in attempt to reproduce the simulation results in 
-@Booth2017.\label{fig:3}](fig4-smoothing.png){ width=100% }
+![Figure 5. Hillshade maps of the 2014 Oso Lanslide region and surface smoothing evolution over 15,000 years predicted by a 
+nonlinear hillslope diffusion model used in the [**nonlineardiff_Landlab.ipynb**](https://github.com/GeoLarryLai/pyTopoComplexity/blob/main/example/nonlineardiff_Landlab.ipynb) 
+notebook, in attempt to reproduce the simulation results in @Booth2017.\label{fig:5}](fig5-smoothing.png){ width=100% }
 
@@
 We extend special thanks to Dr. Eulogio Pardo-Igúzquiza, who generously shared his Fortran code for fractal dimension analysis used in his work 
-@PardoIguzquiza2022b, which significantly inspired the development of the **pyfracd.py** module.
+[@PardoIguzquiza2022b], which  inspired the development of the **pyfracd.py** module.
 

### 2024-08-23 JOSS/paper.rmd

@@
 includes a module for calculating the Terrain Position Index (TPI), a widely used metric that is considered effective 
-in geomorphology research [@Newman2018; @Deumlich2010; @Liu2011]. The TPI is also often used alongside rugosity index 
-calculations in marine geological and ecological analyses [@Wilson2007; @Walbridge2018].
+in geomorphology research [@Newman2018; @Deumlich2010; @Liu2011] and often used alongside Rugosity Index in marine 
+geological and ecological studies [@Wilson2007; @Walbridge2018].
 

### 2024-08-29 setup.py
Add files via upload

@@ -5,7 +5,7 @@ with open("README-pypi.md", "r", encoding="utf-8") as fh:
 
 setup(
     name="pytopocomplexity",
-    version="0.8.0",
+    version="0.8.1",
     author="Larry Syu-Heng Lai",
     author_email="larrysyuhenglai@gmail.com",
     description="A package for topographic complexity analysis",

### 2024-08-29 JOSS/paper.rmd
Add files via upload

@@
    index: 2
-date: 18 August 2024
+date: 30 August 2024
 bibliography: paper.bib
@@
 Index and Terrain Position Index calculations across various spatial scales. This package addresses 
-the scarcity of open-source software for these sophisticated methods, which are crucial in modern 
+the scarcity of open-source software for these sophisticated methods needed in modern 
 terrain analysis, and facilitates data comparison and reproducibility. In the [software respository](https://github.com/GeoLarryLai/pyTopoComplexity.git), 
 we also include a Jupyter Notebook file that integrates components from the Python-based 
-surface-process modeling platform **Landlab** [@Hobley2017]. This allows researchers to 
+surface-process modeling platform **Landlab** [@Hobley2017]. The notebook allows researchers to 
 simulate the smoothing of topography over time through terrestrial nonlinear hillslope 
@@
 critical insights into surface processes and the interactions among the geosphere, biosphere, and 
-hydrosphere. With the increasing availability, utility, and popularity of digital terrain model (DTM) 
-data, quantifying topographic complexity has become an essential measure in terrain analysis across 
+hydrosphere [@Dietrich2006]. With the increasing availability, utility, and popularity of digital terrain model (DTM) 
+data, quantifying topographic complexity has become an essential step in terrain analysis across 
 various research fields. This necessity spans applications such as terrain classification and mapping 
 at various spatial scales [@Weiss2001; @Robbins2018; @Lindsay2019; @PardoIguzquiza2022a], evaluating 
-the depositional age of event sedimentation and subsequent erosion processes 
+the depositional age of event sedimentation (e.g., landslides, alluvial fans) and subsequent erosion processes 
 [@Hetz2016; @Johnstone2018; @Booth2017; @LaHusen2020; @Herzig2023], and identifying habitats to assess 
@@
 of 2D-CWT, fractal dimension, and rugosity index calculations (see Table 1\autoref{tab:1}). Additionally, **pyTopoComplexity** 
-includes a module for calculating the Terrain Position Index (TPI), a widely used metric that is considered effective 
-in geomorphology research [@Newman2018; @Deumlich2010; @Liu2011] and often used alongside Rugosity Index in marine 
+includes a module for calculating the Terrain Position Index (TPI), a widely used metric in geomorphology 
+research [@Newman2018; @Deumlich2010; @Liu2011] and often used alongside Rugosity Index in marine 
 geological and ecological studies [@Wilson2007; @Walbridge2018].
 
-This toolkit can detect the grid spacing and unit of the projected coordinate system (acceptable in meters, 
+This toolkit detects the grid spacing and units of the projected coordinate system (acceptable in meters, 
 U.S. survey feet, and international feet) from the input raster DTM file (GeoTIFF format) and 
-automatically conduct unit conversions in necessary calculation steps to ensure data consistency and 
-reproducibility. Results at nodes affected by edge effects due to no-data values outside the input raster 
-will be removed by default. Users can define the suitable spatial scale to match their research purposes 
+automatically conducts unit conversions in necessary calculation steps to ensure data consistency and 
+reproducibility. Removal of results at nodes affected by edge effects due to no-data values outside the input 
+raster occurs by default. Users can define the suitable spatial scale to match their research purposes 
 and choose computational approaches (e.g., chunk processing, faster mathematical approximations) to 
@@
 | pyrugostiy.py | RugosityIndex | Calculates the Rugosity Index of the land surface | @Jenness2004; @DuPreez2015 |
-| pytpi.py | TPI | Calculate Terrain Position Index of the land or seafloor surface | @Weiss2001; @Walbridge2018 |
+| pytpi.py | TPI | Calculates Terrain Position Index of the land or seafloor surface | @Weiss2001; @Walbridge2018 |
 Table: Table 1 \label{tab:1}: Modules contained in the **pyTopoComplexity** package.
 
-Each module of the **pyTopoComplexity** is provided with a corresponding [example Jupyter Notebook file](https://github.com/GeoLarryLai/pyTopoComplexity/tree/main/example) 
-for usage instructions, using the Light Detection and Ranging (LiDAR) DTM data of a deep-seated landslide that 
-occurred in 2014 in the Oso area of the North Fork Stillaguamish River valley, Washington State, USA 
-[@WashingtonGeologicalSurvey2023]. In the software repository, we also include an additional Jupyter Notebook file 
+Each module of **pyTopoComplexity** includes a corresponding [example Jupyter Notebook file](https://github.com/GeoLarryLai/pyTopoComplexity/tree/main/example)
+with usage instructions. These examples utilize lidar DTM data (~1 m resolution) from the 2014 ‘Oso’ deep-seated landslide
+along the North Fork Stillaguamish River valley in Washington State, USA [@WashingtonGeologicalSurvey2023]. In the software repository, we also include an additional Jupyter Notebook file 
 [**nonlineardiff_Landlab.ipynb**](https://github.com/GeoLarryLai/pyTopoComplexity/blob/main/example/nonlineardiff_Landlab.ipynb), 
@@
 amplitude is distributed across spatial frequencies at each position in the data by transforming spatial data into position-frequency 
-space. This method is particularly effective for depicting the Laplacian of topography [@Torrence1998; @Lashermes2007], revealing 
-concave and convex regions of topography at various scales [@Malamud2001; @Struble2021], identifying deep-seated landslides 
-[@Booth2009; @Berti2013], and estimating the depositional ages of landslide deposits [@Booth2017; @LaHusen2020; @Underwood2022; @Herzig2023].
+space. When used with the Gaussian family of wavelets, this method is particularly effective for depicting the Laplacian of topography 
+[@Torrence1998; @Lashermes2007], revealing concave and convex regions of topography at various smoothing-length scales [@Malamud2001; @Struble2021], 
+identifying deep-seated landslides [@Booth2009; @Berti2013], and estimating the depositional ages of landslide deposits [@Booth2017; @LaHusen2020; @Underwood2022; @Herzig2023].
+
+The **pycwtmexhat.py** module in **pyTopoComplexity** implements the 2D-CWT method for terrain analysis, providing detailed information on how 
+amplitude is distributed across spatial frequencies at each position in the data by transforming spatial data into position-frequency 
+space. When used with the Gaussian family of wavelets, this method is particularly effective for depicting the Laplacian of topography 
+[@Torrence1998; @Lashermes2007], revealing concave and convex regions of topography at various smoothing-length scales [@Malamud2001; @Struble2021], 
+identifying deep-seated landslides [@Booth2009; @Berti2013], and estimating the depositional ages of landslide deposits [@Booth2017; @LaHusen2020; @Underwood2022; @Herzig2023]. 
+Unlike techniques that use moving windows to detect regional topographic complexity, the 2D-CWT method stands out by isolating specific landform features at the scale of the 
+designated $\lambda$ while filtering out noise from terrain variations at longer or shorter wavelengths.
 
@@
 
-, where the resultant wavelet coefficient $C(s,x,y)$ provides a measure of how well the wavelet $\psi$ matches the data $z$ at each grid [@Torrence1998]. 
+, where the resultant wavelet coefficient $C(s,x,y)$ provides a measure of how well the wavelet $\psi$ matches the data $z$ at each grid point [@Torrence1998]. 
 When $s$ is large, $\psi$ is spread out, capturing long-wavelength features of $z$; when $s$ is small, $\psi$ becomes more localized, making it sensitive 
-to fine-scale features of $z$. In this implementation, we use the 2D Mexican Hat wavelet (i.e., Ricker wavelet) function to define $\psi$:
+to fine-scale features of $z$. In this implementation, we use the 2D Ricker or Marr wavelet (i.e., Mexican hat wavelet) function to define $\psi$:
 
@@
 
-The Mexican hat wavelet is proportional to the second derivative of a Gaussian envelope, with its Fourier wavelength ($\lambda$) 
-dependent on the grid spacing ($\Delta$) of the input DTM raster. The wavelet function $\psi$ is scaled according to the 
+The Mexican hat wavelet as defined above is equal to the second derivative of a Gaussian envelope, with its Fourier wavelength ($\lambda$) 
+dependent on the chosen wavelet scale ($s$) and the grid spacing ($\Delta$) of the input DTM raster. The wavelet function $\psi$ is scaled according to the 
 wavelet scale parameter $s$ and the grid spacing $\Delta$, ensuring that the resultant wavelet coefficient $C$ signifies 
@@
 
-We note that the $C$ and $\psi$ equations presented here are the mathmetical approaches adapted in later publications 
-[@LaHusen2020; @Underwood2022; @Herzig2023] and ongoing works [@Booth2023; @Lai2023; @Ozioko2023] of landslide mapping and 
-age dating studies, with minor differences from the earlier similar research in @Booth2009 and @Booth2017 (original MATLAB codes 
-available from [Booth's personal website](https://web.pdx.edu/~boothad/tools.html)). These differences in methatical approach 
-can result $C$ values in different units and order of magnitude (e.g., $10^{-3}$ to $10^{-4}$ [m$^{-2}$] in @Booth2017 
-and prior studies; $10^{-2}$ to $10^{-3}$ [m$^{-1}$] in @LaHusen2020 thereafter). Despite this discrepency, the $C$ values 
+We note that the equations for $C$ and $\psi$ presented here are mathematical approaches adapted in later publications 
+[@LaHusen2020; @Underwood2022; @Herzig2023] and ongoing works on landslide mapping and age dating studies [@Booth2023; @Lai2023; @Ozioko2023]. 
+There are minor differences in the proportionality constant used to define $\psi$ and the conventions used to present the magnitude of the wavelet 
+coefficients $C$, compared to earlier similar research by @Booth2009 and @Booth2017 (original MATLAB codes 
+available from [Booth's personal website](https://web.pdx.edu/~boothad/tools.html)). These differences in methatical approach will by definition 
+result in $C$ values in different units and order of magnitude (e.g., $10^{-3}$ to $10^{-4}$ [m$^{-2}$] in @Booth2017 
+and prior studies; $10^{-2}$ to $10^{-3}$ [m$^{-1}$] in @LaHusen2020 thereafter). Despite this discrepancy, the $C$ values 
 yielded from these two approaches are linearly scaled and interconvertible, and they both reflect identical spatiotemporal patterns 
@@
 the DTM [@Taud2005; @PardoIguzquiza2020; @PardoIguzquiza2022a]. This approach simplifies the problem to estimating the fractal dimension 
-of one-dimensional topographic profiles [@Dubuc1989] within the two-dimensional moving window. For a one-dimensional profile of length $L$, 
+of one-dimensional topographic profiles [@Dubuc1989] within a two-dimensional moving window. For a one-dimensional profile of length $L$, 
 the variogram $\gamma_1(k)$ can be estimated at the $K$ lag distances ($K$ lag distances ($k = 1, \ldots, K$) by:
@@
 The **pyrugosity.py** module in **pyTopoComplexity**  measures the Rugosity Index of the land surface, which is widely used to assess structural 
-complexity of the topography. Such method has been applied in classifying seafloor types by marine geologists and geomorphologist, understanding small-scale 
+complexity of topography and has been applied in classifying seafloor types by marine geologists and geomorphologists, understanding small-scale 
 hydrodynamics by oceanographers, and studying available habitats in the landscape by ecologists and coral biologists [@Lundblad2006; @Wilson2007].
@@
 This module adapts the Triangulated Irregular Networks method from @Jenness2004 to approximate the contoured area as the sum of 
-eight truncated-triangle areas. These triangles connect the central grids, four corner grids, and four grids at the middle points of the 
+eight truncated-triangle areas. These triangles connect the central grid point, four corner grid points, and four grid points at the middle points of the 
 surrounding edges within the moving window. If no local slope correction is applied, the planimetric area is considered to be the horizontal 
 planar area of the moving window, as described in @Jenness2004. Another approach considers slope correction where to the planimetric area is 
-projected onto an plane of the local gradient [@DuPreez2015].
+projected onto a plane of the local gradient [@DuPreez2015].
 
-By definition, the Rugosity Index is as a minimum value of one (completely flate surface). Typical valuesrange of the conventional rugosity 
-index (without slope correction) from one to three although larger values are possible in very steep terrains. The slope-corrected rugosity 
-index, also called arc-chord ratio (ACR) Rugosity Index, could provide a better representation of local surface complexity (Figure 3)\autoref{fig:3}.
+By definition, the Rugosity Index is as a minimum value of one (completely flat surface). Typical values of the conventional rugosity 
+index (without slope correction) range from one to three although larger values are possible in very steep terrains. The slope-corrected rugosity 
+index, also called arc-chord ratio (ACR) Rugosity Index, could provide a better representation of local surface complexity because it is not biased by slope (Figure 3)\autoref{fig:3}.
 
@@
 The **pytpi.py** module in **pyTopoComplexity** calculates the Terrain Position Index (TPI) of the land surface. The TPI, also known as the 
-Topographic Position Index in terrestrial studies [@Weiss2001], measures the relative topographic position of a point compared to its 
-surrounding landforms. This metric highlights regions that are relatively higher or lower than their surroundings, which is useful for 
+Topographic Position Index in terrestrial studies [@Weiss2001], measures the relative topographic elevation of a point compared to those of its 
+surrounding landforms. This metric highlights regions relatively higher or lower than their surroundings, which is useful for 
 distinguishing landscape features such as hilltops, valleys, flat plains, and slopes. In oceanography, an equivalent metric is the 
@@
 
-In this module, the TPI value is computed at the central grid within a square-shaped moving window. Users can specify the size of the moving 
-window (i.e., the number of grids along each edge) to assess the topographic position at different spatial scales. Positive TPI values 
-indicate elevated features, negative values represent depressions, and values close to zero denote flat or gently sloping areas. The **pytpi.py** 
+In this module, the TPI is calculated for the central grid within a square moving window. Users can specify the size of the window (i.e., the 
+number of grids along each edge) to evaluate topographic positions at various spatial scales. Positive TPI values indicate generally convex, 
+elevated features, while negative values represent concave depressions. Values close to zero denote relatively planar areas. The **pytpi.py** 
 module also returns the absolute values of the TPI (Figure 4\autoref{fig:4}). This absolute TPI raster is suggested to be effective for 
@@
 
-## Forward simulation of landscape smoothing through nonlinear hillslope diffusion process
+## Forward simulation of landscape smoothing through nonlinear hillslope diffusion processes
 
@@
 
-, where \(\mathbf{q}_s\) represents the sediment flux at the surface. The sediment flux is further defined by a nonlinear flux law that is 
+, where \(\mathbf{q}_s\) represents the sediment flux at the surface. The sediment flux is further defined by a nonlinear flux law [@Roering1999] that is 
 approximated using a Taylor series expansion [@Ganti2012]:
@@
 
-Here, $\mathbf{S} = -\nabla z$ represents the downslope topographic gradient, and $S$ is its magnitude. The parameter $K$ is a diffusion-like 
-transport coefficient with dimensions of length squared per time. The simulation also incorporates the critical slope gradient ($S_c$) to 
-ensure numerical stability and prevent the numerical instability when $S = S_c$. $N$ denotes the number of terms in the Taylor 
-expansion, while $i$ specifies the number of additional terms included. If $N = 0$, the expression simplifies to linear diffusion [@Culling1963]. 
-The default is set to $N = 2$ that gives the behavior described in @Ganti2012 as an approximation of the nonlinear diffusion.
+Here, $\mathbf{S} = -\nabla z$ represents the downslope topographic gradient, and $S$ is its magnitude. $S_c$ is the critical slope representing the asymptotic 
+maximum hillslope gradient. The parameter $K$ is a diffusion-like transport coefficient with dimensions of length squared per time. 
+$N$ denotes the number of terms in the Taylor expansion, while $i$ specifies the number of additional terms included. If $N = 0$, the expression simplifies to 
+linear diffusion [@Culling1963]. By default, $N$ is set to $2$, that gives the behavior described in @Ganti2012.
 
@@
 and ESRI ASCII formats. Users are required to specify the values for $S_c$, $K$, the length of each time step in years, and the final time to 
-stop the simulation. The example included in the notebook uses LiDAR DTM data from the 2014 Oso Landslide [@WashingtonGeologicalSurvey2023], 
+stop the simulation. The example included in the notebook uses lidar DTM data from the 2014 Oso Landslide [@WashingtonGeologicalSurvey2023], 
 with parameter values provided in @Booth2017, in an attempt to reproduce the simulation results presented in that study (Figure 5\autoref{fig:5}).
@@
 [Cascadia Coastlines and Peoples Hazards Research Hub (Cascadia CoPes Hub)](https://cascadiacopeshub.org), funded by the National Science Foundation Award ([#2103713](https://www.nsf.gov/awardsearch/showAward?AWD_ID=2103713&HistoricalAwards=false)).
-We extend special thanks to Dr. Eulogio Pardo-Igúzquiza, who generously shared his Fortran code for fractal dimension analysis used in his work 
-[@PardoIguzquiza2022b], which  inspired the development of the **pyfracd.py** module.
+We also acknowledge earlier funding by the National Science Foundation to Booth ([#2000188](https://www.nsf.gov/awardsearch/showAward?AWD_ID=2000188&HistoricalAwards=false)) 
+and Duvall ([#1953710](https://www.nsf.gov/awardsearch/showAward?AWD_ID=1953710&HistoricalAwards=false)). We extend special thanks to Dr. Eulogio Pardo-Igúzquiza, 
+who generously shared his Fortran code for fractal dimension analysis used in his work [@PardoIguzquiza2022b], which  inspired the development of the **pyfracd.py** module.
 

### 2024-08-29 JOSS/paper.rmd
Add files via upload

@@
 implementation of four modern methods for quantifying topographic complexity. These methods include 
-two-dimensional continuous wavelet transform (2D-CWT) analysis, fractal dimension estimation, Rugosity 
+two-dimensional continuous wavelet transform analysis, fractal dimension estimation, Rugosity 
 Index and Terrain Position Index calculations across various spatial scales. This package addresses 
@@
 at various spatial scales [@Weiss2001; @Robbins2018; @Lindsay2019; @PardoIguzquiza2022a], evaluating 
-the depositional age of event sedimentation (e.g., landslides, alluvial fans) and subsequent erosion processes 
+the depositional age of event sedimentation (e.g., landslides, avulsion on alluvial fans) and subsequent erosion processes 
 [@Hetz2016; @Johnstone2018; @Booth2017; @LaHusen2020; @Herzig2023], and identifying habitats to assess 
@@
 including two-dimensional continuous wavelet transform (2D-CWT) analysis [@Booth2009; @Berti2013], 
-fractal dimension estimation [@Taud2005; @Robbins2018; @PardoIguzquiza2020], and Rugosity Index 
-calculation [@Jenness2004; @DuPreez2015]. These methods are considered more effective for terrain analysis 
-tasks compared to conventional morphological metrics such as variations in local slope and relief. 
+fractal dimension estimation [@Taud2005; @Glenn2006; @Robbins2018; @PardoIguzquiza2020], and Rugosity Index 
+calculation [@Jenness2004; @DuPreez2015]. These methods are considered more effective for topographic 
+complexity analysis tasks compared to conventional morphological metrics such as variations in local slope and relief. 
 Despite their importance, comprehensive publicly available tools that incorporate these advanced 
@@
 implement basic conventional methods, limiting the reproducibility and comparability of these newer 
-approaches. Although some specialized programs for calculating the Rugosity Index exist [@Walbridge2018; @Benham2022], 
-they have been limited to marine bathymetric studies and involve various mathematical choices and designs.
+approaches. Although specialized programs for calculating the Rugosity Index exist [@Walbridge2018; @Benham2022], 
+they have been confined to marine bathymetric studies and involve various mathematical limitations, assumptions, and designs.
 
@@
 offers computationally efficient and easily customizable implementations for performing and visualizing the results 
-of 2D-CWT, fractal dimension, and rugosity index calculations (see Table 1\autoref{tab:1}). Additionally, **pyTopoComplexity** 
-includes a module for calculating the Terrain Position Index (TPI), a widely used metric in geomorphology 
+of 2D-CWT, fractal dimension, and Rugosity Index calculations (see Table 1\autoref{tab:1}). Additionally, **pyTopoComplexity** 
+includes a module for calculating the Terrain Position Index, a widely used metric in geomorphology 
 research [@Newman2018; @Deumlich2010; @Liu2011] and often used alongside Rugosity Index in marine 
 geological and ecological studies [@Wilson2007; @Walbridge2018].
+
+| Modules  | Classes | Method Descriptions | References |
+| ------------- | ------------- | ------------- | ------------- |
+| pycwtmexhat.py | CWTMexHat | Quantifies the wavelet-based curvature of the land surface using two-dimensional continuous wavelet transform (2D-CWT) with a Mexican Hat wavelet | @Booth2009; @Booth2017 |
+| pyfracd.py | FracD | Conducts fractal dimension analysis on the land surface using variogram procedures | @Wen1997; @PardoIguzquiza2020|
+| pyrugostiy.py | RugosityIndex | Calculates the Rugosity Index of the land surface | @Jenness2004; @DuPreez2015 |
+| pytpi.py | TPI | Calculates Terrain Position Index of the land or seafloor surface | @Weiss2001; @Walbridge2018 |
+Table: Table 1 \label{tab:1}: Modules contained in the **pyTopoComplexity** package.
 
@@
 optimize performance (see details in the **Methods and features overview** section).
-
-| Modules  | Classes | Method Descriptions | References |
-| ------------- | ------------- | ------------- | ------------- |
-| pycwtmexhat.py | CWTMexHat | Quantifies the wavelet-based curvature of the land surface using two-dimensional continuous wavelet transform (2D-CWT) with a Mexican Hat wavelet | @Booth2009; @Booth2017 |
-| pyfracd.py | FracD | Conducts fractal dimension analysis on the land surface using variogram procedures | @Wen1997; @PardoIguzquiza2020|
-| pyrugostiy.py | RugosityIndex | Calculates the Rugosity Index of the land surface | @Jenness2004; @DuPreez2015 |
-| pytpi.py | TPI | Calculates Terrain Position Index of the land or seafloor surface | @Weiss2001; @Walbridge2018 |
-Table: Table 1 \label{tab:1}: Modules contained in the **pyTopoComplexity** package.
 
@@
 
-The **pycwtmexhat.py** module in **pyTopoComplexity** implements the 2D-CWT method for terrain analysis, providing detailed information on how 
-amplitude is distributed across spatial frequencies at each position in the data by transforming spatial data into position-frequency 
-space. When used with the Gaussian family of wavelets, this method is particularly effective for depicting the Laplacian of topography 
-[@Torrence1998; @Lashermes2007], revealing concave and convex regions of topography at various smoothing-length scales [@Malamud2001; @Struble2021], 
-identifying deep-seated landslides [@Booth2009; @Berti2013], and estimating the depositional ages of landslide deposits [@Booth2017; @LaHusen2020; @Underwood2022; @Herzig2023]. 
-Unlike techniques that use moving windows to detect regional topographic complexity, the 2D-CWT method stands out by isolating specific landform features at the scale of the 
-designated $\lambda$ while filtering out noise from terrain variations at longer or shorter wavelengths.
-
 The 2D-CWT is computed by convolving the elevation data $z$ with a wavelet family $\psi$, using a wavelet scale parameter $s$ at every location ($x$, $y$):
@@
 , where the resultant wavelet coefficient $C(s,x,y)$ provides a measure of how well the wavelet $\psi$ matches the data $z$ at each grid point [@Torrence1998]. 
+Unlike other techniques that use moving windows to detect regional topographic complexity, the 2D-CWT method stands out by isolating specific landform features 
+at the scale of the designated wavelength while filtering out noise from terrain variations at longer or shorter wavelengths.
 When $s$ is large, $\psi$ is spread out, capturing long-wavelength features of $z$; when $s$ is small, $\psi$ becomes more localized, making it sensitive
-to fine-scale features of $z$. In this implementation, we use the 2D Ricker or Marr wavelet (i.e., Mexican hat wavelet) function to define $\psi$:
+to fine-scale features of $z$. In this implementation, we use the 2D Ricker or Marr wavelet (i.e., Mexican hat wavelet) function to define $\psi$ [@Ricker1943]:
 
@@
 
-The Mexican hat wavelet as defined above is equal to the second derivative of a Gaussian envelope, with its Fourier wavelength ($\lambda$) 
-dependent on the chosen wavelet scale ($s$) and the grid spacing ($\Delta$) of the input DTM raster. The wavelet function $\psi$ is scaled according to the 
-wavelet scale parameter $s$ and the grid spacing $\Delta$, ensuring that the resultant wavelet coefficient $C$ signifies 
-concave and convex landforms corresponding to the wavelet scale $s$. Users can define the value of $\lambda$ in meters as the 
-targeted spatial scale for landform roughness analysis, and the **pycwtmexhat.py** module will automatically compute the wavelet 
-scale $s$ based on the grid spacing ($\Delta$) of the input raster file (Figure 1)\autoref{fig:1}.
+The Mexican hat wavelet, as defined above, corresponds to the second derivative of a Gaussian envelope. Its Fourier wavelength ($\lambda$) 
+depends on the chosen wavelet scale ($s$) and the grid spacing ($\Delta$) of the input DTM raster. The wavelet function $\psi$ is scaled based on the wavelet 
+scale parameter $s$ and the grid spacing $\Delta$, ensuring that the resultant wavelet coefficient $C$ represents concave and convex landforms according to the 
+wavelet scale $s$. Users can specify the wavelength $\lambda$ in meters as the target spatial scale for landform roughness analysis. The **pycwtmexhat.py** 
+module will automatically compute the wavelet scale $s$ based on the grid spacing ($\Delta$) of the input raster file (Figure 1\autoref{fig:1}). In this module, 
+users can choose to perform convolution either in the original domain (i.e., direct convolution) or in the frequency domain (i.e., using the Fast Fourier Transform) 
+with the `convolve2d` and `fftconvolve` functions from the **SciPy** package, respectively [@2020SciPy-NMeth]. By default, the module uses `fftconvolve` for greater 
+computational efficiency.
 
@@
 coefficients $C$, compared to earlier similar research by @Booth2009 and @Booth2017 (original MATLAB codes 
-available from [Booth's personal website](https://web.pdx.edu/~boothad/tools.html)). These differences in methatical approach will by definition 
+available from [Booth's personal website](https://web.pdx.edu/~boothad/tools.html)). These differences in mathematical approach will by definition 
 result in $C$ values in different units and order of magnitude (e.g., $10^{-3}$ to $10^{-4}$ [m$^{-2}$] in @Booth2017 
@@
 transform (2D-CWT) analysis using the **pycwtmexhat.py** module, with designated Fourier wavelengths ($\lambda$) of the Mexican Hat 
-wavelet at 15 m, 30 m, 45 m, 60 m, and 75 m. \label{fig:1}](fig1-pycwtmexhat.png){ width=100% }
+wavelet at 15 m, 45 m, and 75 m. \label{fig:1}](fig1-pycwtmexhat.png){ width=100% }
 
@@
 
-, where $Z(i)$ is the elevation at location $i$ along the profile. The local fractal dimension ($FD$) is estimated from one-dimensional 
+, where $Z(i)$ is the elevation at location $i$ along the profile. The local fractal dimension ($\text{FD}$) is estimated from one-dimensional 
 profiles in principal directions (i.e., horizontal, vertical, and diagonal) within a square moving window. Assuming that fractional 
@@
 
-, and its exponent $\beta$ is related to the local fractal dimension ($FD$) by:
+, and its exponent $\beta$ is related to the local fractal dimension ($\text{FD}$) by:
 
 $$
-FD = TD + 1 - \frac{\beta}{2}
+\text{FD} = \text{TD} + 1 - \frac{\beta}{2}
 $$
 
-, where $TD$ is the topological dimension in the Euclidean space of the fractional Brownian motion. For one-dimensional fractional Brownian 
-motion, $TD = 1$. The fractal dimension of the two-dimensional surface $(FD)_2^*$ can be estimated as the average fractal dimension of 
-the one-dimensional profiles $(FD)_1^*$:
+, where $\text{TD}$ is the topological dimension in the Euclidean space of the fractional Brownian motion. For one-dimensional fractional Brownian 
+motion, $\text{TD} = 1$. The fractal dimension of the two-dimensional surface $(\text{FD})_2^*$ can be estimated as the average fractal dimension of 
+the one-dimensional profiles $(\text{FD})_1^*$:
 
 $$
-(FD)_2^* = 1 + (FD)_1^*
+(\text{FD})_2^* = 1 + (\text{FD})_1^*
 $$
@@
 $$
-\text{Rugosity Index} = \frac{\text{contoured area}}{\text{planimetric area}}
+\text{Rugosity Index} = \frac{\text{Contoured area}}{\text{Planimetric area}}
 $$
@@
 
-By definition, the Rugosity Index is as a minimum value of one (completely flat surface). Typical values of the conventional rugosity 
+By definition, the Rugosity Index has a minimum value of one (completely flat surface). Typical values of the conventional rugosity 
 index (without slope correction) range from one to three although larger values are possible in very steep terrains. The slope-corrected rugosity 
@@
 
-![Figure 3. Calculated results of the Arc-Chord Ratio Rugosity Index (upper) and the conventional Rugosity Index (lower) for the 2014 Oso Landslide 
-region, using the **pyrugosity.py** module. The calculations were performed with different moving window sizes: 17 by 17 grids (left), 49 by 49 grids 
-(middle), and 83 by 83 grids (right). Grid spacing is 3 U.S. survey feet (approximately 0.9144 meters). \label{fig:3}](fig3-pyrugosity.png){ width=100% }
+![Figure 3. Calculated results of the Arc-Chord Ratio Rugosity Index (left) and the conventional Rugosity Index (right) for the 2014 Oso Landslide 
+region, using the **pyrugosity.py** module. The calculations were performed with different moving window sizes: 17 by 17 grids (top) and 49 by 49 grids 
+(bottom). Grid spacing is 3 U.S. survey feet (approximately 0.9144 meters). \label{fig:3}](fig3-pyrugosity.png){ width=100% }
 
@@
 $$
-TPI = Z_{\text{grid}} - \text{mean}(Z_{\text{neighborhood}})
+\text{TPI} = Z_{\text{grid}} - \text{mean}(Z_{\text{neighborhood}})
 $$
@@
 number of grids along each edge) to evaluate topographic positions at various spatial scales. Positive TPI values indicate generally convex, 
-elevated features, while negative values represent concave depressions. Values close to zero denote relatively planar areas. The **pytpi.py** 
-module also returns the absolute values of the TPI (Figure 4\autoref{fig:4}). This absolute TPI raster is suggested to be effective for 
+elevated features, while negative values represent concave depressions (i.e., saddle features). Values close to zero denote relatively flat surface 
+or area with near continuous slope. The **pytpi.py** module also returns the absolute values of the TPI (Figure 4\autoref{fig:4}). This absolute TPI calculation is suggested to be effective for 
 quick assessments in mapping and relative dating of deep-seated landslide deposits using high-resolution DTM data [@Lai2023].
 
-![Figure 4. Calculated results of the Terrain Position Index (upper) and its absolute values (lower) for the 2014 Oso Landslide region, 
-using the **pytpi.py** module. The calculations were performed with different moving window sizes: 17 by 17 grids (left), 49 by 49 grids 
-(middle), and 83 by 83 grids (right). Grid spacing is 3 U.S. survey feet (approximately 0.9144 meters). \label{fig:4}](fig4-pytpi.png){ width=100% }
+![Figure 4. Calculated results of the Terrain Position Index (left) and its absolute values (right) for the 2014 Oso Landslide region, 
+using the **pytpi.py** module. The calculations were performed with different moving window sizes: 17 by 17 grids (top) and 83 by 83 grids (bottom). 
+Grid spacing is 3 U.S. survey feet (approximately 0.9144 meters). \label{fig:4}](fig4-pytpi.png){ width=100% }
 
